### 2016-05-24 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Minor changes to construction/layout sections in hose stream and gas burner reports

The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 298~mm (11.75~in) depth. Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}. Tongue and grove, 18.3~mm (0.72~in) thick, oriented strand board was screwed to the top of the TJIs.

@@

The second floor of the Two Story Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell. The walls of the second floor were wood framed with nominal 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers. The interior walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board. The exterior walls were protected with 11~mm (0.44~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.

@@

The ceiling height of each structure was approximately 2.4~m (8~ft). The interior dimensions of the Single Story Structure were approximately 6.1~m (20~ft) by 11~m (36~ft), and the interior dimensions of the first and second floors of the Two Story Structure were 5.8~m (19~ft) by 10.7~m (35.1~ft) and 6.1~m (20~ft) by 10.9~m (35.8~ft), respectively. The stairs connecting the two floors of the Two Story Structure started 1.6~m (5.3~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall.

The exterior doorways of each structure and the stairwell doorway on the second level of the Two Story Structure all contained doors that were opened or closed at certain instances during tests to change the ventilation pattern of the structure. All other doorways in the structures did not contain a door. So, in order to close these doorways, a sheet of gypsum board was used to cover the opening, and the doorway remained closed for the duration of the test procedure.
\clearpage

>>>>

The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 298~mm (11.75~in) depth. Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}. Tongue and groove oriented strand board of 18.3~mm (0.72~in) thickness was screwed to the top of the TJIs.

@@

The second floor of the Two Story Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell. The walls of the second floor were wood-frame with nominal 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers. The interior walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board. The exterior walls were protected with 11~mm (0.44~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.

@@

The ceiling height of each structure was approximately 2.4~m (8~ft). The interior dimensions of the Single Story Structure were approximately 6.1~m (20~ft) by 11~m (36~ft), and the interior dimensions of the first and second floors of the Two Story Structure were 5.8~m (19~ft) by 10.7~m (35.1~ft) and 6.1~m (20~ft) by 10.9~m (35.8~ft), respectively. The stairs connecting the two floors of the Two Story Structure started 1.6~m (5.3~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall and contained a 180~mm (7.25~in) rise and 190~mm (7.5~in) run.

The exterior doorways of each structure and the stairwell doorway on the second level of the Two Story Structure all contained doors that were opened or closed at certain instances during tests to change the ventilation pattern of the structure. All other doorways in the structures did not contain a door. In order to close these doorways, a sheet of gypsum board was used to cover the opening, and the doorway remained closed for the duration of the test procedure.
\clearpage

### 2016-05-24 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor changes to construction/layout sections in hose stream and gas burner reports

% ======================
% = EXPERIMENTAL SETUP =
% ======================
\chapter{Experimental Setup}
\label{chap:Experimental_Setup}
The series of field experiments described in this report were conducted in two structures of similar design located at the Delaware County Emergency Services Training Center in Sharon Hill, PA. The fire source for all experiments was generated by three propane burners, and various sensors were used to collect gas temperature, gas velocity, heat flux, and gas concentration measurements throughout the structure.

@@

\begin{figure}[!ht]
	\includegraphics[width=5.25in]{../../Hose_Stream_Tests/Figures/Pictures/east_structure}
	\\~\\
	\includegraphics[width=5.25in]{../../Hose_Stream_Tests/Figures/Pictures/west_structure}
	\caption[North side of the East and West Structures.]{North side of the East (top) and West (bottom) test structures.}
	\label{fig:struct_pics}
\end{figure}

The interior walls of the first floor of each structure were framed with steel studs set to 0.40~m (16~in) centers and track and were lined with 13~mm (0.5~in) thick cement board. The walls were composed of 16~mm (0.625~in) Type X gypsum board. Additionally, the ceiling was composed of two layers of 13~mm (0.5~in) thick cement board.
\FloatBarrier

The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 0.30~m (11.75~in) depth. Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.125~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}. Tongue and grove, 18.3~mm (0.72~in) thick, oriented strand board was screwed to the top of the TJIs.

@@

%SIG FIGS ON DIMENSIONS - ROUND COMMON DECIMALS? Example: 0.625 -> 0.6; 0.75 -> 0.8? They could also be changed to fractions

The second floor of the West Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell. The second story walls were wood framed with 51~mm (2~in) by 102~mm (4~in) studs set to 0.40~m (16~in) centers. The interior walls were protected by 16~mm (0.625~in) fire rated gypsum board, 16~mm (0.625~in) durarock board, and a second layer of 16~mm (0.625~in) fire rated gypsum board. The exterior walls were protected with 11~mm (0.44~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Dimensioned_Full}
	\caption[Dimensioned floor plan of the East Structure.]{Dimensioned floor plan of the East Structure. Structure is symmetric across horizontal centerline.}
	\label{fig:east_dimensioned_plan}
\end{figure}

@@

The interior dimensions of each structure were approximately 6.1~m (20~ft) wide, 11~m (36~ft) long, and 2.4~m (8~ft) high. The stairs connecting the two floors of the West Structure started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall and a 0.18~m (7.25~in) rise and 0.19~m (7.5~in) rise. The exterior doors of both structures, the stairwell door on the second level of the West Structure, and the square roof vent of the East Structure with side length 1.2~m (4~ft) and a depth of 0.32~m (12.75~in) were opened and closed at certain instances during experiments to change the ventilation patterns within the structures.
\FloatBarrier

\section{Instrumentation}
\label{sec:Instrumentation}
The structures were instrumented for temperature, gas velocity, heat flux, and gas concentration measurements. Gas temperatures in the burn rooms were measured with bare-bead, Chromel-Alumel (type K) thermocouples. Additional single thermocouples were installed in conjunction with bi-directional probes for gas velocity measurements. The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples with a 1.0~mm (0.04~in) nominal diameter. The thermocouple wire was protected with an 3.2~mm (0.125~in) diameter inconel sheath. Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer). A radiometer is a total heat flux gauge with a zirconium plate to prevent contributions from convective heat transfer. Calibrated pumps pulled gas samples through a sample conditioning system to eliminate moisture in the sample. Then, the dry gas sample was piped to a series of gas analyzers and the concentrations of oxygen, carbon monoxide, and carbon dioxide were measured. A legend is presented in Fig.~\ref{fig:Instrumentation_Legend} to clarify the instrumentation schematics presented in the follow sections.

@@

\begin{figure}[!ht]
	\includegraphics[width=0.9\columnwidth]{../Figures/Pictures/burners}
	\caption[Three propane burners.]{Three propane burners used as the fuel source for the experiments at a position of 0.6~m (2~ft) off the south and west walls of the East Structure.}
	\label{fig:burners}
\end{figure}

>>>>

% ======================
% = EXPERIMENTAL SETUP =
% ======================
\chapter{Experimental Setup}
\label{chap:Experimental_Setup}
The series of field experiments described in this report were conducted in two structures of similar design located at the Delaware County Emergency Services Training Center in Sharon Hill, PA. Three propane burners were used to provide the fire source for all experiments, and various sensors were used to collect gas temperature, gas velocity, heat flux, and gas concentration measurements throughout the structure.

@@

\begin{figure}[!ht]
	\includegraphics[width=5.25in]{../../Hose_Stream_Tests/Figures/Pictures/east_structure}
	\\~\\
	\includegraphics[width=5.25in]{../../Hose_Stream_Tests/Figures/Pictures/west_structure}
	\caption[North side of the East and West Structures.]{North side of the East Structure (top) and West Structure (bottom).}
	\label{fig:struct_pics}
\end{figure}

The interior walls of the first floor of each structure were framed with steel studs set to 400~mm (16~in) centers and track and were lined with 13~mm (0.5~in) thick cement board. The walls were composed of 16~mm (0.63~in) Type X gypsum board. Additionally, the ceiling was composed of two layers of 13~mm (0.5~in) thick cement board.
\FloatBarrier

The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 298~mm (11.75~in) depth. Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}. Tongue and groove oriented strand board of 18.3~mm (0.72~in) thickness was screwed to the top of the TJIs.

@@

The second floor of the West Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell. The second story walls were of wood-frame with 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers. The interior walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board. The exterior walls were protected with 11~mm (0.44~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Dimensioned_Full}
	\caption[Dimensioned floor plan of the East Structure.]{Dimensioned floor plan of the East Structure. Structure dimensions are symmetric across horizontal centerline.}
	\label{fig:east_dimensioned_plan}
\end{figure}

@@

The ceiling height of each structure was approximately 2.4~m (8~ft). The interior dimensions of the East Structure were approximately 6.1~m (20~ft) by 11~m (36~ft), and the interior dimensions of the first and second floors of the West Structure were 5.8~m (19~ft) by 10.7~m (35.1~ft) and 6.1~m (20~ft) by 10.9~m (35.8~ft), respectively. The stairs connecting the two floors of the West Structure started 1.6~m (5.3~ft) off the interior south wall with a width of 1.2~m (4~ft) off the interior east wall and contained a 180~mm (7.25~in) rise and 190~mm (7.5~in) run. The exterior doors of both structures, the stairwell door on the second level of the West Structure, and the square roof vent in the East Structure with a 1.2~m (4~ft) side length and 320~mm (12.75~in) depth were opened and closed at certain instances during experiments to change the ventilation patterns within the structures.
\FloatBarrier

\section{Instrumentation}
\label{sec:Instrumentation}
The structures were instrumented for temperature, gas velocity, heat flux, and gas concentration measurements. Gas temperatures in the burn rooms were measured with bare-bead, Chromel-Alumel (type K) thermocouples. Additional single thermocouples were installed in conjunction with bi-directional probes for gas velocity measurements. The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples with a 1.0~mm (0.04~in) nominal diameter. The thermocouple wire was protected with an 3.2~mm (0.13~in) diameter inconel sheath. Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer). A radiometer is a total heat flux gauge with a zirconium plate to prevent contributions from convective heat transfer. Calibrated pumps pulled gas samples through a sample conditioning system to eliminate moisture in the sample. Then, the dry gas sample was piped to a series of gas analyzers and the concentrations of oxygen, carbon monoxide, and carbon dioxide were measured. A legend is presented in Fig.~\ref{fig:Instrumentation_Legend} to clarify the instrumentation schematics presented in the follow sections.

@@

\begin{figure}[!ht]
	\includegraphics[width=0.9\columnwidth]{../Figures/Pictures/burners}
	\caption[Three propane burners.]{Three propane burners located 0.6~m (2~ft) off the south and west interior walls of the first floor provided the fire source for the experiments.}
	\label{fig:burners}
\end{figure}
